Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
fix minor typo - remove an 's'

OWL is used to determine whether projects are both internally consistent, with
all objects having an explicit RDF type, and whether they are consistent with
the ontologies that they import. The main points that PODD focuses on for
validation is determining that mappings are consistent with the basic PODD
predicates and classes, so that they can be used to render both static HTML
pages and provide HTML based editing facilities. For example, any OWL object
property that has been defined to link from image acquisition runs to images can
be used to define the purpose of an image. This may include any combination of
the defined properties, without requiring all of the properties to be used.
% The parent object types and properties used by PODD to establish basic ground
% rules for rendering and validation are defined in a small base schema ontology.
General scientific properties and phenotype specific properties are defined
in larger extension ontologies as illustrated in Figure~\ref{poddontologies}.

>>>>

OWL is used to determine whether projects are both internally consistent, with
all objects having an explicit RDF type, and whether they are consistent with
the ontologies that they import. The main point that PODD focuses on for
validation is determining that mappings are consistent with the basic PODD
predicates and classes, so that they can be used to render both static HTML
pages and provide HTML based editing facilities. For example, any OWL object
property that has been defined to link from image acquisition runs to images can
be used to define the purpose of an image. This may include any combination of
the defined properties, without requiring all of the properties to be used.
% The parent object types and properties used by PODD to establish basic ground
% rules for rendering and validation are defined in a small base schema ontology.
General scientific properties and phenotype specific properties are defined
in larger extension ontologies as illustrated in Figure~\ref{poddontologies}.
